How One Microtask Affects Another

### 2016-01-04 docs/publications/2015.12_CHI/man.tex
more revisions to manuscript (minor)

To investigate the phenomenon in a
highly generalizable setting, we sought a task that would involve 
qualitative judgment and enable relatively unconstrained responses. 
We also sought a task that would be a typical exemplar of the kinds of
tasks actually seen on microtask platforms (see 
Table~\ref{table:task_composition} for examples).  For this purpose, we 
adopted
image-labeling as a canonical microtask, a task in which workers provide 
descriptive labels to images using free-text inputs.  Image labeling is
a qualitative task without clearly ``correct'' or ``incorrect'' responses,
and is among the most common kinds of tasks on MTurk 
(see Table \ref{table:task_composition}).
If task-induced priming arises in our 
setup, it could be expected in a large number of microtasks and 
crowdsourced workflows where workers are called upon to provide qualitative
judgment.

@@

As a point of comparison, we also conducted framing experiments, 
in which we altered the framing of microtask assignments, in terms of the 
stated purpose of the task, or by naming the funder.
Remarkably, the effects of prior microtasks,
which are virtually ubiquitous, are on par with, or stronger than, 
the effects of overtly framing an assignment.

@@

In a somewhat related vein, other researchers investigated 
the effects of task-switching \cite{yin2014monetary}.  During 
\textit{switch-tasks} (tasks which differ in nature from the immediately 
preceeding task), workers were more inclined to make mistakes, 
and took longer to complete the task.  
However, the reserchers found that by offering a performance-based
bonus, which paid if workers completed the task quickly and correctly,
performance during switch-tasks was both faster and more accurate.

@@

We can establish Inequality~\ref{eq:sup:l1} by considering an
optimal classifier having accuracy $\eta_*$.  
Let us assume that workers are shown 
$\mathrm{design}_1$ or $\mathrm{design}_2$ with equal probability.
If the worker gives the response $x$, the opitimal classifier must guess
that the worker was shown the design most likely to elicit $x$.
In other words, if $p_i(x)$ is the probability that a worker shown 
$\mathrm{design}_i$ responds with $x$, then it is optimal to 
guess that the worker saw $\mathrm{design}_j$, where 
$j = \arg\max_j{p_j(x)}$.

@@

\paragraph{Existence of intertask and framing effects.} 
Looking at the frequencies with which workers used words, we tested for
heterogeneity between the two treatments of each sub-experiment.
For the intertask sub-experiment, we found the responses 
for the two treatments differed significantly 
(by $\chi^2$ test, $p<0.001$), 
demonstrating that intertask effects do exist.  However, we did not find 
significant effects due to framing ($p=0.29$) 
(Figure~\ref{fig:theta}A).

Testing for heterogeneity of word-frequencies was based on 
Pearson's $\chi^2$ test with Yates' correction.
In linguistics applications, the use of a $\chi^2$ to test for 
heterogeneity between corpora has been called
into question, because there is frequently heterogeneity \textit{within}
a given corpus \cite{kilgarriff1996comparing}.
This occurs because certain documents in a corpus will regard certain 
topics, leading to bursty word usage.  While our setup is substantially
remote from the applications for which this concern was raised, 
one could argue that the responses to a given treatment
constitute a ``corpus'', and the responses of a given worker to a 
``document''.
To address this concern, we randomly split responses to given treatment
into two sets, and tested for hetererogeneity between the sets.
In all cases, we failed to find heterogeneity \textit{within} a given 
treatment (with $p > 0.3$ for all treatments and $p > 0.8$ for most).
These results hold for Experiment 2, to be discussed later.
Thus, the heterogeneity we observed \textit{between} the intertask 
treatments indicates a meaningful effect.

@@

The results from the first experiment clearly show that intertask effects 
arise and are strong.  On the other hand, we were scarcely able to observe
any effect due to framing.  This raises a few questions which we seek
to answer using a second experiment.  The first question is simply whether
the result will replicate using different sets of images.  
If so, then as the next question, we may ask how intertask effects evolve
as the worker performs tasks.  Presumbaly, intertask effects wear off at 
some point, but is it after one task, two, or more?

@@

In setting up Experiment 2, we also wish to increase the strength of 
framing.  While finding that intertask effects were stronger than framing 
was surprising and remarkable, perhaps the most meaningful comparison
would be one which shows just how extreme framing treatments need to be 
to produce effects on par with intertask effects.  
One factor that may have weakened the effects of framing in Experiment 1 
is the inclusion of initial tasks between the framing slide and the test 
tasks. They were included to ensure that workers had always completed the
same number of tasks before begining the test tasks.  However, their 
inclusion gives time for differential framing effects to 
subside, while also generating intertask effects that are 
\textit{shared} between the treatments, potentially masking the framing 
effects that remain.  In the next experiment, we measure framing effects 
immediately after the application of framing.

\pagebreak
\section{Experiment 2}
\subsection{Setup}
In Experiment 2 we again had ``intertask'' and ``framing'' 
sub-experiments, but we included a third sub-experiment, ``echo'', which 
incorporated more extreme framing treatments.  
As before, each sub-experiment had
two treatments, but this time they were ``food'' and ``objects''.
Keeping a food treatment enabled us to perform deeper lexical analysis of 
both experiments (discussed in the results for Experiment 2).  
The experiment was again performed using a single HIT on MTurk, 
and involved 1666 workers.
Workers were randomly assigned to a sub-experiment and treatment upon
starting the HIT.

@@

In contrast to Experiment 1, we performed five replicates of the intertask
sub-experiment, each time permuting the test tasks.  The test tasks were
``rotated'' in such a way that, what was the first test task became
the second, the second became the third, and so on up until the last test
task, which became the first.  In this way, each of the five positions
was occupied by each test task, enabling us to disentangle the effect of
test task position (relative to initial tasks) from test task content,
and thereby see how intertask effects vary as a function of position.

The framing sub-experiment was similar to that from Experiment 1, except
that we omitted initial tasks altogether, so that the test tasks followed
immediately after framing.  This meant that workers would not have 
performed any tasks by the time they begin the test tasks.  While that will
hold constant for both framing treatments, and thus not produce a 
differential effect, the workers may be more (or less) susceptible to 
influences during their first few tasks.  One can expect framing effects
to be stronger than in Experiment 1, because of the immediacy with which
the test tasks follow the framing.  The framing slide for the food 
treatment read ``Funded by the laboratory for the visual perception of 
Food and Ingredients'', and for the objects treatment it read ``\ldots
perception of Objects and Tools''.

@@

\paragraph{Existence and strength of effects.}
As in the previous experiment, intertask effects led to significant 
changes in the words workers used to labele images in the intertask 
sub-experiment ($p<0.001$).  Based on
the performance of a naive Bayes classifier, the strength of the effect 
was (as a lower bound) $\theta=30.6\%$ total variational distance
(see Figure~\ref{fig:theta}A).  Again, it is difficult to visualize the 
distributions of word frequencies, but for reference, the distributions 
shown in Figure~\ref{fig:l1_example}B have $\theta = 30\%$.

@@

\begin{figure}
	\centering
	\includegraphics[scale=0.87]{figs/specificity.pdf}
	\caption{
		Workers exposed to food (either in framing or initial tasks)
		show a different tendency to focus on food when labeling
		test tasks, and their vocabulary in reference to food is affected.
		In all three plots, positive values indicate a larger quantity for 
		workers from the food treatment.
		(\textbf{A}) Exposing workers to food does not necessarily increase
		the fraction of food references they provide during test tasks.
		(\textbf{B}) The number of unique food-related
		words (richness) was greater for food-exposed workers, 
		except in the 
		case of the framing sub-experiment of Experiment 1 
		(stars indicate the threshold
		for a significant deviation, $\alpha=0.05$). 
		(\textbf{C}) Food-exposed
		workers used more specialized words to refer to food.
		Standard error bars are shown in (\textbf{A}) and (\textbf{C}).
	}
	\label{fig:specificity}
\end{figure}

@@

Using the automated labeling of food words, we found that, contrary to
expectations,
workers exposed to food (via prior tasks or framing) did not necessarily
use more food-words when labeling images in the test tasks.
In the intertask treatment of Experiment 1, workers from the food treatment
actually used significantly\footnote{
  Frequencies of food references within a treatment were calculated as
  an average across workers, and modeled as normally distributed.
} \textit{fewer} food-related words 
during test tasks (Figure~\ref{fig:specificity}A).  This finding
rules out a seemingly-simple idea that workers emphasize
content seen in earlier tasks.  Seeing given content does significantly 
influence workers' propensity to refer to it in subsequent tasks, but it 
does not necessarily \textit{increase} it.

To deepen our understanding, we investigated workers' lexical richness in 
reference to food, that is, the number of \textit{unique} food-related 
words used.  Even if workers provide an abundance of food-related words, 
there can be less diversity, if, for example, workers repeat generic 
references to food.
The \textit{intertask} sub-experiments from both Experiments 1 and 2 showed
that workers from the food treatments had
greater lexical richness, in reference to food, than their counterparts 
(as much as 20\% more) (Figure~\ref{fig:specificity}B).  
This is particularly noteworthy for Experiment 1, because there,
workers from the food treatment made fewer total references to food.  
Thus, although prior task exposure does not necessarily increase the 
propensity
to identify content in later tasks, it does appear to activate vocabulary 
pertaining to content in the prior tasks.

@@

The above observations regarding lexical richness, suggest that initial 
tasks might influence workers to use more \textit{refined} or 
\textit{specialized} words, when referring to aspects 
of content that had been present in the initial tasks.  
To test this directly, we used the hypernym and hyponym relations in 
WordNet to operationalize the notion of word specialization.  
Within each sub-experiment, we determined the relative specificity
of the food-words, between the treatments using the following equation:
\begin{equation}
	S(P,Q) = \frac{
		\sum_{w\in P}\sum_{v\in Q} \left(
			\mathbf{1}_{[w>v]} - \mathbf{1}_{[v>w]} \right)
	}{
		\sum_{w\in P}\sum_{v\in Q} \left(
			\mathbf{1}_{[w>v]} + \mathbf{1}_{[v>w]} \right)
	},
\end{equation}
where $P$ and $Q$ are sets of words associated to different experimental 
treatments, and $\mathbf{1}_{[w>v]}$ evaluates
to 1 if word $w$ is more specific than (i.e. is a hyponym of) word $v$.
The relative specificity lies within $[-1,1]$; 
we report it as a percentage.
In computing this quantity between two treatments, we first computed the 
relative specificity for the treatments separately for each test task, and 
averaged the results obtained across the five test tasks.  To establish
significance, we again used a null model, based on bootstrapping.

In all sub-experiments except for Experiment 1 framing sub-experiment, 
workers from the food treatment used significantly more specialized words, 
in reference to food 
(about 15\% more; $p < 0.05$) (Figure~\ref{fig:specificity}C).
It is interesting that such substantial increases in both the lexical 
richness and specialization of food-related words 
held for the intertask sub-experiment of Experiment 1, where, as mentioned,
we observed 
that food-exposed workers made \textit{fewer} references to food overall. 
These observations point 
to countervailing factors: one factor tending to activate the more 
specialized and less common food-related words 
(yielding greater lexical richness and specialization), and the other tending 
to suppress certain, presumably more common and generic words 
(yielding fewer food-related words in total).

This hypothesis is corroborated when we look at those words whose 
frequencies changed the most from one treatment to another 
(Table~\ref{table:top-words}).  
The word ``food'', which is the most generic possible food-related word, was 
always \textit{suppressed} among food-primed workers.  In fact, 
for all experiments, ``food'' was the \textit{most suppressed} word.

@@

While our setup does not allow us to tell what psychological mechanism(s) 
are responsible for intertask effects, we suspect that priming is involved.
As mentioned, we believe microtasks create conditions conducive to priming,
and this is what first lead us to suspect intertask effects might exist.  
Priming occurs when a prior stimulus causes a person to respond to a 
subsequent task with increased speed or 
accuracy, or with the ability to recognize briefer or 
noisier stimuli \cite{BJOP1796,BJOP1826,Huber2008324}.
In the case of image labeling, pre-activation of 
vocabulary relating to prior tasks, through a priming mechanism, 
could lead to more rapid retrieval of those words in subsequent tasks.  
A worker may be more likely to enter those words which enter her mind 
first, so priming could lead to certain words being prefered.  
As the worker
completes many tasks with a common theme, the worker's vocabulary relating
to that theme will be increasingly activated, enabling more specialized
words to be retrieved quickly, and therefore to be submitted as responses.

However, as we aluded to above, there appears to be countervailing factors:
while richness and specialization always increased (or were not 
significantly changed), the total number of references to content in 
prior tasks was observed to significantly increase in most cases, but
it significantly decreased in one.  Here we suspect 
\textit{negative} priming to be at play.
Negative priming occurs when, after exposure to a stimulus 
considered to be non-salient, subsequent recognition of the stimulus is 
inhibited \cite{mayr2007negative}.  In the case of our image labeling 
tasks, repeated exposure to images depicting food may cause the worker to 
stop regarding the basic presence of food as salient, and direct their 
attention instead to the features that are specific to the food in a given 
image.  This could lead the worker to suppress very generic references to 
food (as we observed for the words ``food'', ``meal'', ``dinner'', see 
Table~\ref{table:top-words}).  This could hold even when, due to positive
priming, more specialized food-related words are activated.
The balance of these factors would determine whether the worker makes 
more references to food overall.  This would explain the paradoxical
changes in number of references to food, along with the observed 
changes to the richness and specificity of workers' food-related 
vocabulary.

>>>>

To investigate the phenomenon in a
highly generalizable setting, we sought a task that would involve 
qualitative judgment and enable relatively unconstrained responses. 
We also sought a task that would be a typical exemplar of the kinds of
tasks actually seen on microtask platforms (see 
Table~\ref{table:task_composition} for examples).  For this purpose, we 
adopted
image-labeling as a canonical microtask, a task in which workers provide 
descriptive labels to images using free-text inputs.  Image labeling is
a qualitative task without clearly ``correct'' or ``incorrect'' responses,
and is among the most common kinds of tasks on MTurk 
(see Table \ref{table:task_composition}).
If effects from earlier tasks arise in our setup, similar effects could be 
expected in 
a large number of microtasks and crowdsourced workflows where workers are 
called upon to provide qualitative judgment.

@@

As a point of comparison, we also conduct framing experiments, 
in which we alter the framing of microtask assignments, in terms of the 
stated purpose of the task, or by naming the funder.
Remarkably, the effects of prior microtasks,
which are virtually ubiquitous, are on par with, or stronger than, 
the effects of overtly framing an assignment.

@@

In a somewhat related vein, other researchers investigated 
the effects of task-switching \cite{yin2014monetary}.  During 
\textit{switch-tasks} (tasks which differ in nature from the immediately 
preceding task), workers were more inclined to make mistakes, 
and took longer to complete the task.  
However, the researchers found that by offering a performance-based
bonus, which paid if workers completed the task quickly and correctly,
performance during switch-tasks was both faster and more accurate.

@@

We can establish Inequality~\ref{eq:sup:l1} by considering an
optimal classifier having accuracy $\eta_*$.  
Let us assume that workers are shown 
$\mathrm{design}_1$ or $\mathrm{design}_2$ with equal probability.
If the worker gives the response $x$, the optimal classifier must guess
that the worker was shown the design most likely to elicit $x$.
In other words, if $p_i(x)$ is the probability that a worker shown 
$\mathrm{design}_i$ responds with $x$, then it is optimal to 
guess that the worker saw $\mathrm{design}_j$, where 
$j = \arg\max_j{p_j(x)}$.

@@

\paragraph{Existence of intertask and framing effects.} 
Looking at the frequencies with which workers used words, we tested for
heterogeneity between the two treatments of each sub-experiment.
For the intertask sub-experiment, we found the responses 
for the two treatments differed significantly 
(by $\chi^2$ test, $p<0.001$), 
demonstrating that intertask effects do exist.  However, we did not find 
significant effects due to framing ($p=0.29$).

Testing for heterogeneity of word-frequencies was based on 
Pearson's $\chi^2$ test with Yates' correction.
In linguistics applications, the use of a $\chi^2$ to test for 
heterogeneity between corpora has been called
into question, because there is frequently heterogeneity \textit{within}
a given corpus \cite{kilgarriff1996comparing}.
This occurs because certain documents in a corpus will regard certain 
topics, leading to bursty word usage.  While our setup is substantially
remote from the applications for which this concern was raised, 
one could argue that the responses to a given treatment
constitute a ``corpus'', and the responses of a given worker to a 
``document''.
To address this concern, we randomly split responses to given treatment
into two sets, and tested for heterogeneity between the sets.
In all cases, we failed to find heterogeneity \textit{within} a given 
treatment (with $p > 0.3$ for all treatments and $p > 0.8$ for most).
These results hold for Experiment 2, to be discussed later.
Thus, the heterogeneity we observed \textit{between} the intertask 
treatments indicates a meaningful effect.

@@

The results from the first experiment clearly show that intertask effects 
arise and are strong.  On the other hand, we were scarcely able to observe
any effect due to framing.  This raises a few questions which we seek
to answer using a second experiment.  The first question is simply whether
the result will replicate using different sets of images.  
If so, then as the next question, we may ask how intertask effects evolve
as the worker performs tasks.  Presumably, intertask effects wear off at 
some point, but is it after one task, two, or more?

@@

In setting up Experiment 2, we also wish to increase the strength of 
framing.  While it was remarkable that intertask effects were stronger 
than the framing effects elicited in the first experiment, perhaps the 
most meaningful comparison is one which shows just how extreme framing 
treatments need to be to produce effects on par with intertask effects.  
One factor that may have weakened the effects of framing in Experiment 1 
is the inclusion of initial tasks between the framing slide and the test 
tasks. They were included to ensure that workers had always completed the
same number of tasks before beginning the test tasks.  However, their 
inclusion gives time for differential framing effects to 
subside, while also generating intertask effects that are 
\textit{shared} between the treatments, potentially masking the framing 
effects that remain.  In the next experiment, we measure framing effects 
immediately after the application of framing.

\pagebreak
\section{Experiment 2}
\subsection{Setup}
In Experiment 2 we again had ``intertask'' and ``framing'' 
sub-experiments, but we included a third sub-experiment, ``echo'', which 
incorporated more extreme framing treatments.  
As before, each sub-experiment had
two treatments, but this time they were ``food'' and ``objects''.
Keeping a food treatment enabled us to perform deeper lexical analysis of 
both experiments (to be discussed in the results for Experiment 2).  
The experiment was again performed using a single HIT on MTurk, 
and involved 1666 workers.
Workers were randomly assigned to a sub-experiment and treatment upon
starting the HIT.

@@

In contrast to Experiment 1, we performed five replicates of the intertask
sub-experiment, each time permuting the test tasks.  The test tasks were
``rotated'' in such a way that, what was the first test task became
the second, the second became the third, and so on up until the last test
task, which became the first.  In this way, each of the five positions
was occupied by each test task, enabling us to disentangle the effect of
test task position (relative to initial tasks) from test task content,
and thereby see how intertask effects vary as a function of position in
the task sequence.

The framing sub-experiment was similar to that from Experiment 1, except
that we omitted initial tasks altogether, so that the test tasks followed
immediately after framing.  This meant that workers would not have 
performed any tasks by the time they began the test tasks.  While that will
hold constant for both framing treatments, and thus not produce a 
differential effect, the workers may be more (or less) susceptible to 
influences during their first few tasks.  One can expect framing effects
to be stronger than in Experiment 1, because of the immediacy with which
the test tasks follow the framing.  The framing slide for the food 
treatment read ``Funded by the laboratory for the visual perception of 
Food and Ingredients'', and for the objects treatment it read ``\ldots
perception of Objects and Tools''.

@@

\paragraph{Existence and strength of effects.}
As in the previous experiment, intertask effects led to significant 
changes in the words workers used to label images in the intertask 
sub-experiment ($p<0.001$).  Based on
the performance of a naive Bayes classifier, the strength of the effect 
was (as a lower bound) $\theta=30.6\%$ total variational distance
(see Figure~\ref{fig:theta}A).  Again, it is difficult to visualize the 
distributions of word frequencies, but for reference, the distributions 
shown in Figure~\ref{fig:l1_example}B have $\theta = 30\%$.

@@

\begin{figure}
	\centering
	\includegraphics[scale=1.05]{figs/specificity.pdf}
	\caption{
		Workers exposed to food (either in framing or initial tasks)
		show a different tendency to focus on food when labeling
		test tasks, and their vocabulary in reference to food is affected.
		In all three plots, positive values indicate a larger quantity for 
		workers from the food treatment.
		(\textbf{A}) Exposing workers to food does not necessarily increase
		the fraction of food references they provide during test tasks.
		(\textbf{B}) The number of unique food-related
		words (richness) was greater for food-exposed workers, 
		except in the 
		case of the framing sub-experiment of Experiment 1 
		(stars indicate the threshold
		for a significant deviation, $\alpha=0.05$). 
		(\textbf{C}) Food-exposed
		workers used more specialized words to refer to food.
		Standard error bars are shown in (\textbf{A}) and (\textbf{C}).
	}
	\label{fig:specificity}
\end{figure}

@@

Using the automated labeling of food words, we found that, contrary to
expectations,
workers exposed to food (via prior tasks or framing) did not necessarily
use more food-words when labeling images in the test tasks.
In the intertask treatment of Experiment 1, workers from the food treatment
actually used significantly\footnote{
  Frequencies of food references within a treatment were calculated as
  an average across workers, and modeled as normally distributed.
} \textit{fewer} food-related words 
during test tasks (Figure~\ref{fig:specificity}A).  This finding
rules out a seemingly-simple idea that workers emphasize
content seen in earlier tasks.  Seeing given content significantly 
influences workers' propensity to refer to it in subsequent tasks, but it 
does not necessarily \textit{increase} it.

To deepen our understanding, we investigated workers' lexical richness in 
reference to food, that is, the number of \textit{unique} food-related 
words used.  Even if workers provide an abundance of food-related words, 
there can be less diversity, if, for example, workers repeat generic 
references to food.
The \textit{intertask} sub-experiments from both Experiments 1 and 2 showed
that workers from the food treatments had
greater lexical richness, in reference to food, than their counterparts 
(as much as 20\% more) (Figure~\ref{fig:specificity}B).  
This is particularly noteworthy for the intertask sub-experiment in 
Experiment 1, because there,
workers from the food treatment made fewer total references to food.  
Thus, although prior task exposure does not necessarily increase the 
propensity
to identify content in later tasks, it does appear to activate vocabulary 
pertaining to content in the prior tasks.

@@

The above observations regarding lexical richness, suggest that initial 
tasks might influence workers to use more \textit{refined} or 
\textit{specialized} words, when referring to aspects 
of content that had been present in the initial tasks.  
To test this directly, we used the hypernym and hyponym relations in 
WordNet to operationalize the notion of word specialization.  
Within each sub-experiment, we determined the relative specificity
of the food-words, between the treatments using the following equation:
\begin{equation}
	S(P,Q) = \frac{
		\sum_{w\in P}\sum_{v\in Q} \left(
			\mathbf{1}_{[w>v]} - \mathbf{1}_{[v>w]} \right)
	}{
		\sum_{w\in P}\sum_{v\in Q} \left(
			\mathbf{1}_{[w>v]} + \mathbf{1}_{[v>w]} \right)
	},
\end{equation}
where $P$ and $Q$ are sets of words associated to different experimental 
treatments, and $\mathbf{1}_{[w>v]}$ evaluates
to 1 if word $w$ is more specific than (i.e. is a hyponym of) word $v$.
The relative specificity lies within $[-1,1]$; 
we report it as a signed percentage.
In computing this quantity between two treatments, we first computed the 
relative specificity for the treatments separately for each test task, and 
averaged the results obtained across the five test tasks.  To establish
significance, we again used a null model, based on bootstrapping.

In all sub-experiments,
workers from the food treatment used more specialized words, 
in reference to food 
(about 15\% more; $p < 0.05$) (Figure~\ref{fig:specificity}C).
Except in the case of the framing treatment of Experiment 1, these 
between-treatment differences in word specialization were significant 
($p<0.05$).

It is interesting that such substantial increases in both the lexical 
richness and specialization of food-related words 
held for the intertask sub-experiment of Experiment 1, where, as mentioned,
we observed 
that food-exposed workers made \textit{fewer} references to food overall. 
These observations point 
to countervailing factors: one factor tending to activate the more 
specialized and less common food-related words 
(yielding greater lexical richness and specialization), and the other tending 
to suppress certain, presumably more common and generic words 
(yielding fewer food-related words in total).

This hypothesis is corroborated when we look at those words whose 
frequencies changed the most from one treatment to another 
(Table~\ref{table:top-words}).  
The word ``food'', which is the most generic possible food-related word, 
was always \textit{suppressed} among food-exposed workers, along with other
very generic food references being suppressed too, such as ``meal'' and 
``dinner''.  In fact, 
for all experiments, ``food'' was the \textit{most suppressed} word.
Meanwhile, the most activated food-related words, among food-exposed 
workers, tended to refer to specific foods, 
like ``apple'', ``cheese'', and ``bread''.

@@

While our setup does not allow us to tell what psychological mechanism(s) 
are responsible for intertask effects, we suspect that priming is involved.
As mentioned, we believe microtasks create conditions conducive to priming,
and this is what first lead us to suspect intertask effects might exist.  
Priming occurs when a prior stimulus causes a person to respond to a 
subsequent task with increased speed or 
accuracy, or with the ability to recognize briefer or 
noisier stimuli \cite{BJOP1796,BJOP1826,Huber2008324}.
In the case of image labeling, pre-activation of 
vocabulary relating to prior tasks, through a priming mechanism, 
could lead to more rapid retrieval of those words in subsequent tasks.  
A worker may be more likely to enter those words which enter her mind 
first, so priming could lead to certain words being preferred.  
As the worker
completes many tasks with a common theme, the worker's vocabulary relating
to that theme will be increasingly activated, enabling more specialized
words to be retrieved quickly, and therefore to be submitted as responses.

However, as we alluded to above, there appears to be countervailing 
factors:
while richness and specialization of food-related words always increased 
(or were not significantly changed) among workers exposed to food in 
initial tasks, the total number of references to food significantly 
\textit{decreased} in one case.  
Here we suspect \textit{negative} priming to be at play.
Negative priming occurs when, after exposure to a stimulus 
considered to be non-salient, subsequent recognition of the stimulus is 
inhibited \cite{mayr2007negative}.  In the case of our image labeling 
tasks, repeated exposure to images depicting food might cause the worker to
stop regarding the basic presence of food as salient, and to direct her 
attention instead to the features that are specific to the food in a given 
image.  This would explain the suppression very generic references to 
food observed in Table~\ref{table:top-words}.  
The balance between the inhibition of generic food-related words, with 
activation of specific ones could lead to more or less food references
overall, so this dual priming mechanism is consistent with our 
observations.  Direct experimentation would be needed to determine whether
priming mechanisms, positive or negative, are in able to explain intertask
effects.
